---
title: "Congress Data Report"
author: "Haoxi Ma"
date: "4/18/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import data and load some packages
```{r message=FALSE}
setwd("/Users/mahaoxi/Desktop/project/Congress data management")
load("Congress99.RData")
library(ggplot2)
library(mice)
library(plotrix)
library(maps)
library(dplyr)
```

## Check data property

### 1.Test missing value
```{r,fig.show='hide'}
md.pattern(dat99)
```
There is no missing value

### 2.Show data structure
```{r}
str(dat99)
names(dat99)
```
There is no missing value but have some "" value and in facotr, this correspond to redundancy levels

## Arrange data in two tables
```{r}
Table1<-dat99[,c("vote_legislator.text","vote_legislator.party","vote_legislator.state",
                 "roll_number")]
names(Table1)<-c("Name","Party","State","roll-number")
Table2<-dat99[,c("roll_number","issue","question","title_or_description","vote_result")]
names(Table2)<-c("roll-number","issue number","question","title/description","votes")
```

## Question1
```{r}
congress.member<-Table1[!duplicated(Table1$Name),]
str(congress.member)#there is "" value in Party and state
levels(congress.member$Party)
congress.member<-congress.member[congress.member$Party!="",]
congress.member<-congress.member[congress.member$State!="",]
#delete redundancy levels
congress.member$Party<-factor(congress.member$Party)
congress.member$State<-factor(congress.member$State)
```
### results
```{r}
table(congress.member$Party)
```

## Question2
```{r}
ggplot(data=congress.member,aes(x=State))+geom_bar(aes(fill=Party))
```

```{r}
table(congress.member[c("Party","State")])
```

## Question3
We only consider the Yea and Nay in voting results
```{r}
#function that when same vote_result in R and D, give x=1 else x=0
Sel<-function(x){
  dat.D<-dat99 %>% filter(roll_number==x) %>% filter(vote_legislator.party=="D")
  dat.R<-dat99 %>% filter(roll_number==x) %>% filter(vote_legislator.party=="R")
  tab.D<-table(dat.D["vote_result"]);tab.R<-table(dat.R["vote_result"])
  ifelse(tab.D["Yea"]>tab.D["Nay"],result.D<-"Agree",result.D<-"Disagree")
  ifelse(tab.R["Yea"]>tab.R["Nay"],result.R<-"Agree",result.R<-"Disagree")
  ifelse(result.D!=result.R,x<-0,x<-1)
}
sketch<-seq(1,611,1);sketch<-unlist(lapply(sketch,Sel));
index<-seq(1,611,1)[sketch==0];
index
```
Now we get the roll number which D and R make different decisions and take #609 as an example
```{r}
dat609.D<-dat99 %>% filter(roll_number==609) %>% filter(vote_legislator.party=="D")
dat609.R<-dat99 %>% filter(roll_number==609) %>% filter(vote_legislator.party=="R")
table(dat609.D["vote_result"])
```
So there are 207 people in Democratic Party having propensity in #609 roll number
```{r}
table(dat609.R["vote_result"])
```
So there are 217 people in Republican Party having propensity in #609 roll number

## Question4
### (1)
```{r}
levels(dat99$result)
res<-dat99[dat99$result!="",]
res$result<-factor(res$result)
res<-res[!duplicated(res$roll_number),]
tabular<-as.data.frame(table(res$result))
num_P<-tabular$Freq[which(tabular$Var1=="P")]
num_F<-tabular$Freq[which(tabular$Var1=="F")]
num_other<-sum(tabular$Freq[which(tabular$Var1!="P"&tabular$Var1!="F")])
number<-c(num_P,num_F,num_other);Name<-c("Passed","Failed","Other")
pct<-round(number/sum(number)*100,digit=1)
lbls<-paste(Name,pct) %>% paste("%",sep="")
pie3D(number,labels=lbls,col=rainbow(length(lbls)),main="Vote Results",theta = pi/4)
```

```{r}
table(sketch)
```
So #76 votes were determined by party affiliations

## Question5
```{r}
Table2<-Table2[which(Table2$`issue number`!="" & Table2$votes!=""),]
Table2$`issue number`<-factor(Table2$`issue number`)
Table2$votes<-factor(Table2$votes)
iss.votes<-as.data.frame.matrix(table(Table2[c("issue number","votes")]))
iss.votes
```

## Draw a plot for states corresponding to #congress member
```{r}
member<-as.data.frame(table(congress.member$State))
names(member)<-c("region","number")
#order the region
member$region<-factor(member$region,levels=state.abb)
levels(member$region)<-state.name
member$region<-tolower(as.character(member$region))
map_state<-map_data("state")
num.member<-left_join(map_state,member,by="region")
mhx<-ggplot(num.member,aes(long,lat,group=group))+geom_polygon(aes(fill=number),color="white")+
      scale_fill_viridis_c(option="C")+labs(title="#Congress members of states")+
      theme(axis.text = element_blank(),axis.ticks = element_blank(),
            axis.title = element_blank())
mhx
```

```{r}
rm(list=ls())
```
















